### 2021-07-08 README.Rmd
Functions added to aid conditioning. No EWN

@@

* 2021-06-28 aMSE 0.0.0.2000 The AMSE can now conduct what are effectively retrospective analyses. This is affected by changing the 'CATCHES, 47, if>1 this is the number of historical catch years' line in the control.csv file, which can now be done in a loop using the new 'changevar' function. This has necessitated also changing the 'CEYRS, 20, The first year of catches for which there are CPUE records, ie 1992 is 20th year of catches', which used to take a direct value of how any years of CPUE data there are. We could have just changed two numbers but along that path errors lay.

>>>>

* 2021_07-04 aMSE 0.0.0.1500 Another big change. Functions added to aid conditioning, and aspects of the projections streamlined.  No errors, warnings, or notes

@@
